Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-09-07 stp/paper_aaai/main.tex
changed example a bit after some feedback, so it's clearer now

\subsubsection{Example} Consider the situation where we have some simple relational database tables with columns $\langle$\textit{Surname, Workplace, Date}$\rangle$, and 
$\langle$\textit{Company, Event, Begin, Until, Location}$\rangle$.
We do not \textit{a priori} know if ``Date'' in the first table is a 
date of birth or the date a person started working; or whether the 
``Location'' on the second table refers to the location of the event, or the 
address of the company. 
Given an ontology like the one in Fig. \ref{FIG:onto}, we would like to automatically map the new data sources to classes of the 
ontology.\hfill$\square$

>>>>

\subsubsection{Example} Consider the situation where we have some simple relational database tables with columns $\langle$\textit{Surname, Event, Date}$\rangle$, and 
$\langle$\textit{Company, Festival, Address}$\rangle$.
We do not \textit{a priori} know if ``Date'' is a 
date of birth of the person or the start date of the event (c.f. Fig. \ref{FIG:onto}); or whether 
``Address'' refers to the name of the place where the festival is located, or the 
email address of the company. 
Given an ontology like the one in Fig. \ref{FIG:onto}, we would like to automatically map the new data sources to  the 
ontology.\hfill$\square$
